%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Jason Tsao} \\ \vspace{1pt}
    \href{mailto:jason.p.tsao@sjsu.edu}{\underline{jason.p.tsao@sjsu.edu}} $|$ 
    \href{https://linkedin.com/in/jtsaoo/}{\underline{linkedin.com/in/jtsaoo}} $|$
    \href{https://github.com/Maaboudoufu/}{\underline{github.com/maaboudoufu}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {San Jose State University}{San Jose, CA}
      {Bachelor of Science in Computer Engineering, Minor in Japanese (GPA 3.65)}{Aug. 2024 -- June 2028}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework:} Programming Concepts \& Methodology; Object-Oriented Concepts \& Methodology; Assembly Language Programming; Introduction to Circuit Analysis; Linear Algebra; Multivariable Calculus}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Information Technology Technician}{Feb. 2026 -- Present}
      {Student Union, Inc. of SJSU}{San Jose, CA}
      \resumeItemListStart
        \resumeItem{Maintained and troubleshot Windows/Mac systems, Active Directory, and Windows Server infrastructure; supported workstation deployment, imaging, and patch management for a student body of 40,000.}
        \resumeItem{Developed PowerShell scripts to automate system administration tasks including OS upgrades, patch deployment, software installations, and routine maintenance processes.}
        \resumeItem{Supported network connectivity (TCP/IP, DHCP, DNS) and infrastructure including switches, firewalls, and printers; managed SSL certificate installations and secure reverse proxy HTTPS connections via IIS.}
        \resumeItem{Utilized Qualys, Sophos Central, Jamf, and Intune for endpoint security monitoring, vulnerability remediation, and device compliance; deployed Zabbix on Linux for infrastructure monitoring with custom triggers and alerting.}
        \resumeItem{Used Lansweeper for ticketing, asset tracking, and system inventory; maintained detailed documentation of hardware, software, and IT procedures.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\textbf{\href{https://github.com/Nayab-23/SeedHackathon}{StudyGuard}} $|$ \emph{Python, FastAPI, OpenCV, OpenAI Whisper, SQLAlchemy, NVIDIA Jetson Orin Nano}}{}
            \resumeItemListStart
                \resumeItem{Awarded \textbf{2nd Place} at the Seeed Embodied AI Hackathon; built a focus-monitoring system with a dynamically changing DNS server and Reachy Mini robot for supervision.}
                \resumeItem{Developed a classification pipeline with OpenCV and GPT-4V classifying focus states every 10s, streaming live video to a FastAPI dashboard, with a Whisper-powered voice agent driving robot gestures and dnsmasq allowlist updates.}
            \resumeItemListEnd
        \resumeProjectHeading
            {\textbf{\href{https://github.com/Maaboudoufu/spotipi}{Spotipi}} $|$ \emph{React, TypeScript, Vite, Tailwind CSS, Node.js, Express, Prisma, SQLite}}{}
            \resumeItemListStart
                \resumeItem{Built a full-stack web application enabling multiple authorized users to control a shared Spotify account through a unified interface with real-time playback management, queue browsing, catalog search, and role-based access control (Admin, DJ, Viewer) secured with bcrypt hashing, AES-encrypted token storage, and audit logging.}
                \resumeItem{Built a CI/CD pipeline with GitHub Actions using a post-push deploy script that SSHs into an Oracle VPS to pull, install dependencies, generate Prisma schemas, build both workspaces, and restart the app with PM2.}
            \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Home Lab} $|$ \emph{WireGuard, Pi-hole, Nginx, Vaultwarden, Docker, Cloudflare}}{}
          \resumeItemListStart
            \resumeItem{Implemented a WireGuard VPN on Oracle VPS for private mesh-style networking with an Nginx reverse proxy and SSL/TLS certificates via Cloudflare; self-hosted Vaultwarden and Ollama with Docker Compose.}
            \resumeItem{Integrated the local Ollama instance with OpenClaw to build an always-on AI agent that automates daily workflows including scheduling, email triage, and task management across messaging platforms.}
          \resumeItemListEnd

    \resumeSubHeadingListEnd


%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C/C++, Assembly, JavaScript, HTML/CSS, Bash/Zsh, PowerShell} \\
     \textbf{Frameworks \& Libraries}{: React.js, Node.js, FastAPI, SQLAlchemy} \\
     \textbf{Infrastructure \& DevOps}{: TCP/IP, DHCP, DNS, VLAN, VPN (WireGuard), Nginx, SSL/TLS, Docker, Linux System Administration, Git, GitHub Actions, CI/CD} \\
     \textbf{Security \& Endpoint Management}{: Qualys, Sophos Central, Jamf, Intune, Active Directory, Windows Server} \\
     \textbf{Certifications}{: Technical Support Fundamentals (Google); Vulnerability Management Detection and Response (Qualys)} \\
     \textbf{Spoken Languages}{: English (Native) $|$ Japanese (Limited Working Proficiency) $|$ Chinese (Elementary Proficiency)} \\
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
